\begin{longtable}{>{\centering\arraybackslash}p{2cm}|
                  p{5.5cm}
                  p{5.5cm}}
    \hline
    \rowcolor{gray!30} % header row shading
    \textbf{Month} & \multicolumn{1}{c}{\textbf{Programming}} & \multicolumn{1}{c}{\textbf{Thesis}} \\
    \hline
    \endfirsthead

    \hline
    \rowcolor{gray!30} % repeated header row shading
    \textbf{Month} & \multicolumn{1}{c}{\textbf{Programming}} & \multicolumn{1}{c}{\textbf{Thesis}} \\
    \hline
    \endhead

    \hline
    \endfoot

    \hline
    \endlastfoot

\rowcolors{2}{gray!15}{white}

August & Finalise code for generating the initial training set based on varying \gls{sfh}. & Finalise and submit the research proposal. \\

September & Train the first iteration of \tc on the \gls{sfh} library. Implement $k$-fold cross-validation for performance assessment. & Refine Literature Review and Methodology chapters based on initial practical work. \\

October & Analyse model performance and optimise training set parameters (e.g., the number of \glspl{ssp}). Implement goodness-of-match tests. & Begin drafting the Results chapter, detailing the setup and performance of the \gls{sfh}-only model. \\

November & Test the trained model using real and/or other simulated galaxy spectra and compare output. & Continue writing and refining the initial Results chapter. \\

December & Begin development for adding complexity to the training set, starting with incorporating metallicity as a second parameter. & Consolidate all results for the \gls{sfh}-only model. Draft a preliminary discussion in preparation for the mid-year report. \\

January & Generate the new, more complex training library that varies both \gls{sfh} and metallicity. & Write up the full methodology and results for the completed \gls{sfh}-only model for mid-year submission. \\

February & Train \tc on the complex library. Obtain and analyse preliminary results for this more advanced model. & Compile and submit the progress report at the end of the month, including full results for the \gls{sfh} model and preliminary findings for the complex model. \\

March & Finalise all analysis of the complex model. Compare its performance against the simpler model and draw final conclusions from the programming work. & Write the complete Results and Discussion sections, incorporating the final analysis of the complex model. \\

April & Finalise all code and documentation. Ensure all figures for the thesis are complete and polished. If ahead on all of this, consider adding dust into model. & Draft the Abstract and Conclusion. Assemble all chapters into the first complete, formal thesis draft. \\

May & Submit draft code, then fix analysis based on draft feedback. & Submit and then incorporate feedback. Focus on editing, proofreading, and formatting the thesis document. \\

June & Finalise and submit code repository. & Final read-through and submission of the Honours thesis and presentation. \\
\end{longtable}